Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-29 Article/main.tex
Updated refs

As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals. This will be accomplished through studying literature in the relevant fields and identifying the instances where it is viable.

@@

\\
\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.37]{merrill2.png}}
\caption{Own Image summarising Merrill's First Principles}
\label{fig}
\end{figure}
\\
The principles and corollaries provided by Merrill\cite{Merrill2002} provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.  It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
Another important factor to consider is how to keep learners engaged and motivated with the instructional material. One model for motivating learners is the ARCS Model which was developed by John Keller\cite{keller1987development} which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}. It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a, keller1987development}. 
The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a, keller1987development}.
Relevance refers to having the content be relevant to the learner\cite{keller1987development} and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge\cite{keller1987development}.
Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a, keller1987development}. This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a, keller1987development}.
The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a, keller1987development}. This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a, keller1987development}.

@@

\begin{itemize}
\item Declarative Knowledge is usually comprised of facts and jargon within a topic.
\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor.
\item Rules-Based Knowledge is strict statements linking concepts.
\item Procedural Knowledge is a progression based path to reach an outcome.
\item Soft Skills are general strategies for dealing with various social interactions.
\item Affective Knowledge deals with topics about subjective phenomena such as emotions.
\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this).
\end{itemize}

@@

>>>>

As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals. This will be accomplished through studying literature in the relevant fields and identifying the instances where it is viable. The primary question aimed to be answered by this study is \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.37]{merrill2.png}}
\caption{Own Image summarising Merrill's First Principles}
\label{fig}
\end{figure}

The principles and corollaries provided by Merrill\cite{Merrill2002} provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.  It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
\\\\
Another important factor to consider is how to keep learners engaged and motivated with the instructional material. One model for motivating learners is the ARCS Model which was developed by John Keller\cite{keller1987development} which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}. It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a, keller1987development}. 
\\\\
The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a, keller1987development}.
\\\\
Relevance refers to having the content be relevant to the learner\cite{keller1987development} and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge\cite{keller1987development}.
\\\\
Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a, keller1987development}. This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a, keller1987development}.
\\\\
The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a, keller1987development}. This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a, keller1987development}.

@@

\begin{itemize}
\item Declarative Knowledge is usually comprised of facts and jargon within a topic.\\
\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor.\\
\item Rules-Based Knowledge is strict statements linking concepts.\\
\item Procedural Knowledge is a progression based path to reach an outcome.\\
\item Soft Skills are general strategies for dealing with various social interactions.\\
\item Affective Knowledge deals with topics about subjective phenomena such as emotions.\\
\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this).
\end{itemize}

@@

While this case study made use of instructional theory targeted towards preschool children\cite{allers2021children, callaghan2018}
